\section{Related Work}
\label{sec:related}

Many systems have been proposed to help managing distributed
applications. Plush, appmanager are two management systems
which support deploy, maintain and monitor applications
centrally. Plush supports automatic bootstrap
(self-deployment) of client end, but the centralized
approach limit their scalability. Plush-M further improved
Plush's scalability by replacing star topology in Plush with
RanSub. 

Researchers have been studing self-* properties of
distributed systems for long time. Self-stabalization is a
concept of fault-tolerance in distributed computing. A
self-stabalization system will converge to a legitimate
state from \emph{any} state. DHTs are distributed systems
that have self-oranizing properties. It will automatically
orgnize their topologies as predefined topologies under
changing network conditions. \cite{self-host} proposed
self-hosting systems that acquire or release resources
dynamically and automatically deploy the system to acquired
resources (as real or virtual machines) using underling
system management tools.

\comment{
DHT (self-organization), 

Dependable Self-Hosting Distributed Systems Using Constraints
self-stabalization

19. E.W. Dijkstra, "Self-Stabilizing Systems in Spite of Distributed Control," Comm.
ACM, vol. 17, no. 11, 1974, pp. 643-644.

20. S. Dolev, Self-Stabilization, MIT Press, 2000.

plush LASCO provides improved scalability and fault
tolerance
}



% vim:foldmethod=marker:textwidth=60
