\section{Related Work}
\label{sec:related}

Many systems have been proposed to help managing distributed
applications. Plush~\cite{Albrecht2007} is a management
system which support deploying, monitoring and controlling
applications centrally. Plush can bootstrap
(self-deployment) its clients automatically, but the
centralized approach limits its scalability.
Plush-M~\cite{Topilski2008} further improved Plush's
scalability on managing applications by replacing star
topology in Plush with RanSub~\cite{Kostic2003}, but the
management of Plush clients is still in centralized
approach. SMON addresses the self-management property of
distributed systems using epidemic algorithm. It can be used
to manage other management systems efficiently.

Researchers have been studying self-* properties of
distributed systems for long time.
Self-stabilization~\cite{Dijkstra1974} is a concept of
fault-tolerance in distributed computing. A
self-stabilization system will converge to a legitimate
state from any state. DHTs~\cite{Stoica2001, Ratnasamy2001,
Rowstron2001} are distributed systems that have
self-organizing properties. They will automatically organize
their overlay topologies conforming to predefined
constraints under changing network conditions.
\cite{Yin2008} proposed self-hosting system that acquires or
releases resources dynamically and automatically deploys the
system to acquired resources (as real or virtual machines)
using underling system management tools. SMON is
complementary to these systems and these techniques can be
combined together to build distributed systems which is more
stable and efficient with little human management efforts.

\comment{
DHT (self-organization),

Dependable Self-Hosting Distributed Systems Using Constraints
self-stabalization

19. E.W. Dijkstra, "Self-Stabilizing Systems in Spite of Distributed Control," Comm.
ACM, vol. 17, no. 11, 1974, pp. 643-644.

20. S. Dolev, Self-Stabilization, MIT Press, 2000.

plush LASCO provides improved scalability and fault
tolerance
}



% vim:foldmethod=marker:textwidth=60
